Manuscript draft

### 2019-09-10 manuscript/Discussion_KAT.Rmd
Update Discussion_KAT.Rmd

[Variation in how much variability is explained by climate-- hard to say if this is methodological or real. discuss methodological limitations, also local allocation gradients.]

@@

Related to this, we find that climate more strongly explains variation in the major fluxes, with lower levels of variation explained in subsidiary fluxes. Although this could in part be related to a lack of standardisation in methodology across studies, as discussed above, it could also indicate that factors other than climate have significant influence over subsidiary fluxes. This is consistent with the results we find for allocation between fluxes: although climate has a significant influence on subsidiary fluxes, it is not the only factor that is important, and many other local- and regional-scale factors  influence the way carbon is allocated between subsidiary fluxes. We would expect that this would reduce the strength of the effect of climate on subsidiary fluxes.

>>>>

-- hard to say if this is methodological or real. discuss methodological limitations, also local allocation gradients.]

One interesting observation was that climate explains more variation in the major fluxes (**LIST**) than in subsidiary fluxes (**LIST**) (Fig. 2; **some SI table?**). There are two non-exclusive potential explanations for this. First, it may be that methodological variation is larger relative to flux magnitude for some of the subsidiary fluxes. Belowground fluxes in particular are difficult to quantify, and measurement methods for the belowground fluxes considered here may be measured through fundamentally different approaches (*e.g.*, **ingrowth cores, XXX for $BNPP_{fine root}$; root exclusion, stable isotope tracking, or gas exchange of excised roots for $R_root$**), and sampling depth is variable and often insufficient to capture the full soil profile. $ANPP_{woody stem}$, which is also poorly explained by latitude or climate, is more straightforward to measure but is subject to variability introduced by differences such as biomass allometries applied, minimum plant size sampled, and exclusion or inclusion of branch fall (**REF**). However, methodological variation and uncertainty affects all of fluxes considered here, and some of the larger fluxes that vary more strongly with respect to climate (ANPP, NPP) are estimated by summing uncertain component fluxes. Second, variation in the proportion of variability explained by climate could also indicate that factors other than climate have significant influence over subsidiary fluxes. This is consistent with the results we find for allocation between fluxes: although climate has a significant influence on subsidiary fluxes, it is not the only factor that is important, and many other local- and regional-scale factors  influence the way carbon is allocated between subsidiary fluxes. We would expect that this would reduce the strength of the effect of climate on subsidiary fluxes. [**work on this second part, add refs**]

@@
